---
title: "FC Metrics Susceptibility to Motion- Gordon ICA Fix Only"
output:
  html_document:
    toc: true
    theme: united
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(psych)
library(gam)
library(summarytools)
library(PerformanceAnalytics)
library(ppcor)
library(reshape2)
library(ggplot2)
library(R.matlab)
library(Hmisc)
```
# All runs averaged together

```{r load data, include=FALSE}
data_dir="~/Documents/projects/in_progress/arun_fc_metrics_motion/"
dropbox_data="~/Dropbox/projects/in_progress/arun_fc_metrics_motion/output/data/Gordon_ICA_FIX/"
run1_data=read.csv(paste0(dropbox_data, "modularity_raw_REST1_LR_060319.csv"))
run2_data=read.csv(paste0(dropbox_data, "modularity_raw_REST1_RL_060319.csv"))
run3_data=read.csv(paste0(dropbox_data, "modularity_raw_REST2_LR_060319.csv"))
run4_data=read.csv(paste0(dropbox_data, "modularity_raw_REST2_RL_060319.csv"))
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
```

## Do partial correlations for each run and average them together

```{r load data, include=FALSE}
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_LR/"
motiondata1 <- read.csv(paste0(mydir,"/rfMRI_REST1_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data1 <- data.frame(subject_list, run1_data)
alldata1 <- merge(modul_data1, motiondata1, by = "subject", all = TRUE)
alldata1 <- alldata1 %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
alldata1$Age_numeric <- dplyr::recode(alldata1$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
alldata1$Gender_numeric <- recode(alldata1$Gender, "M"=1, "F" = 2)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_RL/"
motiondata2 <- read.csv(paste0(mydir,"/rfMRI_REST1_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data2 <- data.frame(subject_list, run2_data)
alldata2 <- merge(modul_data2, motiondata2, by = "subject", all = TRUE)
alldata2 <- alldata2 %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
alldata2$Age_numeric <- dplyr::recode(alldata2$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
alldata2$Gender_numeric <- recode(alldata2$Gender, "M"=1, "F" = 2)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_LR/"
motiondata3 <- read.csv(paste0(mydir,"/rfMRI_REST2_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data3 <- data.frame(subject_list, run3_data)
alldata3 <- merge(modul_data3, motiondata3, by = "subject", all = TRUE)
alldata3 <- alldata3 %>% filter(., num_communities_Pearson != 0)
alldata3 <- na.omit(alldata3)
#recode age to be the median of the bins that are provided
alldata3$Age_numeric <- dplyr::recode(alldata3$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
alldata3$Gender_numeric <- recode(alldata3$Gender, "M"=1, "F" = 2)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_RL/"
motiondata4 <- read.csv(paste0(mydir,"/rfMRI_REST2_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data4 <- data.frame(subject_list, run4_data)
alldata4 <- merge(modul_data4, motiondata4, by = "subject", all = TRUE)
alldata4 <- alldata4 %>% filter(., num_communities_Pearson != 0)
alldata4 <- na.omit(alldata4)
#recode age to be the median of the bins that are provided
alldata4$Age_numeric <- dplyr::recode(alldata4$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
alldata4$Gender_numeric <- recode(alldata4$Gender, "M"=1, "F" = 2)
```

## Just plot raw modularity across metrics

```{r plot of raw modularity across different metrics}
#Make a barplot of abs value modularity
toplot <- dplyr::select(alldata4,modul_Pearson, modul_Spearman, modul_Coherence:modul_MutualInformationTime) 
toplot <- melt(toplot)
p<-ggplot(toplot, aes(x=variable, y=value, fill=variable)) + 
  geom_bar(width = 0.4, position = position_dodge(width=0.5), stat="summary", fun.y=mean)+ 
  theme_classic() 
p
+ labs(title="100-node Yeo parcellation",x="Baseline Edge weight distribution", y = "Modularity quality index Q")+ theme(plot.title = element_text(hjust = 0.5))+ theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))

metrics=c("Pearson", "Spearman", "Coherence", "WaveletCoherence", "MutualInformation","MutualInformationTime")
#calculate the relationship between raw modularity and motion for each of the 4 runs
for (i in 1:4){
  assign("data",get(paste0("alldata",i)))
  mean_modul=numeric(6)
   for (l in 1:6){
    assign("metric", metrics[l])
    temp <- data %>% dplyr::select(.,matches(paste0("^modul_",metric,"$")))
    # print(colnames(temp))
    # temp2 <- cbind(temp$Age_numeric, temp[3])
    mean_modul[l]<- mean(temp[,1])
     
   }
    assign(paste0("mean_modul_estimate_run",i),data.frame(mean_modul, metrics))
}
#beeswarm plot
#Melt them together
all <- cbind(mean_modul_estimate_run1, mean_modul_estimate_run2, mean_modul_estimate_run3, mean_modul_estimate_run4)
all$metrics <- factor(all$metrics, levels=c("Pearson", "Spearman", "Coherence", "WaveletCoherence", "MutualInformation","MutualInformationTime"), labels=c("P", "S", "MIT", "C","WC", "MIF") )
colnames(all) <- c("estimate1", "metrics", "estimate2","metrics", "estimate3", "metrics","estimate4", "metrics")
all <- melt(all, id.vars = "metrics")
#Plot them like Arun, using his colors
p<-ggplot(all, aes(x=metrics, y=value, color=metrics)) + 
  geom_jitter(position=position_jitter(0.2), cex=3)
p + theme_classic() + stat_summary(fun.data="mean_sdl",fun.args = list(mult = 1) ,
                 geom="pointrange", shape=95, cex=1) + labs(title="333-node Gordon parcellation",x="", y = "Modularity quality index (Q)")+ theme(plot.title = element_text(hjust = 0.5), legend.position = "none")+ theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14)) +scale_color_manual(values=c("#0072BD", "#D95319", "#EDB120", "#7E2F8E", "#77AC30", "#4DBEEE"))
```


## Raw modularity and motion correlations

```{r modularity motion, echo=TRUE}

#calculate the relationship between raw modularity and motion for each of the 4 runs
for (i in 1:4){
  assign("data",get(paste0("alldata",i)))
  rawcorr_modul<- lapply(data[12:17], function(eachFormula) {cor.test(eachFormula, data$motion, method="kendall")})
  rawcorr_modul_estimate<- lapply(data[12:17], function(eachFormula) {cor.test(eachFormula, data$motion, method="kendall")$estimate})
  motionavgweight_corr_estimate <- lapply(data[6:11], function(eachFormula) {cor.test(eachFormula, data$motion, method="kendall")$estimate})
  rawmotionmodul_corr <- data.frame(names(data)[12:17], unlist(rawcorr_modul_estimate))
  motionavgweight_corr <- data.frame(names(data)[6:11], unlist(motionavgweight_corr_estimate))
  assign(paste0("rawmotioncorr_tauestimate_run",i),rawmotionmodul_corr)
  assign(paste0("motionavgweight_corr_run",i),motionavgweight_corr)
}


#average them together
averaged_rawmotioncorr_acrossruns <- numeric()
averaged_rawmotioncorr_acrossruns$estimate <-(rawmotioncorr_tauestimate_run1$unlist.rawcorr_modul_estimate.+rawmotioncorr_tauestimate_run2$unlist.rawcorr_modul_estimate.+rawmotioncorr_tauestimate_run3$unlist.rawcorr_modul_estimate.+rawmotioncorr_tauestimate_run4$unlist.rawcorr_modul_estimate.)/4
averaged_rawmotioncorr_acrossruns$names <- unlist(strsplit(names(alldata1)[12:17], "_"))[2*(1:length(names(alldata1[,12:17])))]

barplot(averaged_rawmotioncorr_acrossruns$estimate, names.arg =averaged_rawmotioncorr_acrossruns$names, ylim=c(0, -0.08), col="blue", cex.axis=1.5, cex.names=1)

```

## Modularity and motion, controlling for avg weight
Also examine avg weight and motion.
```{r controlling for avgweight modul, echo=TRUE}
metrics=c("Pearson", "Spearman", "Coherence", "WaveletCoherence", "MutualInformation","MutualInformationTime")
#calculate the relationship between modularity and motion controlling for avg weight for each of 4 runs
alldata1 <- alldata1 %>% dplyr::select(.,-contains("num_communities")) %>% dplyr::select(.,-contains("allgamma"))
alldata2 <- alldata2 %>% dplyr::select(.,-contains("num_communities")) %>% dplyr::select(.,-contains("allgamma"))
alldata3 <- alldata3 %>% dplyr::select(.,-contains("num_communities")) %>% dplyr::select(.,-contains("allgamma"))
alldata4 <- alldata4 %>% dplyr::select(.,-contains("num_communities")) %>% dplyr::select(.,-contains("allgamma"))
for (i in 1:4){
  assign("data",get(paste0("alldata",i)))
  pcorr_modul_estimate=numeric(6)
  for (l in 1:6){
    assign("metric", metrics[l])
    temp <- data %>% dplyr::select(.,matches(paste0("_",metric,"$")),matches("motion"))
    print(colnames(temp))
    pcorr_modul_estimate[l] <- as.numeric(pcor.test(temp[2], temp[3], temp[1], method="kendall")$estimate)
  }
  assign(paste0("pcorr_modul_estimate_run",i),as.data.frame(pcorr_modul_estimate, metrics))
  
}
#Melt them together
all <- cbind(pcorr_modul_estimate_run1, pcorr_modul_estimate_run2, pcorr_modul_estimate_run3, pcorr_modul_estimate_run4)
all$metrics <- factor(metrics, levels=c("Pearson", "Spearman", "Coherence", "WaveletCoherence", "MutualInformation","MutualInformationTime"), labels=c("P", "S", "MIT", "C","WC", "MIF") )
colnames(all) <- c("estimate1", "estimate2", "estimate3", "estimate4", "metrics")
all <- melt(all, id.vars = "metrics")
#Plot them like Arun, using his colors
p<-ggplot(all, aes(x=metrics, y=value, color=metrics)) + 
  geom_jitter(position=position_jitter(0), cex=2)
p + theme_classic() + stat_summary(fun.data="mean_sdl",fun.args = list(mult = 1) ,
                 geom="pointrange", shape=18, cex=1.3) + labs(title="333-node Gordon parcellation",x="", y = "Partial correlation of Q with motion")+ theme(plot.title = element_text(hjust = 0.5))+ theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14)) +scale_color_manual(values=c("#0072BD", "#D95319", "#EDB120", "#7E2F8E", "#77AC30", "#4DBEEE"))+ylim(-.125,0)

#average them together
averaged_pcormotion_acrossruns <-(pcorr_modul_estimate_run1$pcorr_modul_estimate+pcorr_modul_estimate_run2$pcorr_modul_estimate+pcorr_modul_estimate_run3$pcorr_modul_estimate+pcorr_modul_estimate_run4$pcorr_modul_estimate)/4
averaged_pcormotion_acrossruns <- as.data.frame(averaged_pcormotion_acrossruns)
averaged_pcormotion_acrossruns$names <- metrics

barplot(averaged_pcormotion_acrossruns$averaged_pcormotion_acrossruns, names.arg =averaged_pcormotion_acrossruns$names, ylim=c(0.01, -0.08), col="purple", cex.axis=1.5, cex.names=1)
```


## Modularity and motion, controlling for age and sex (as numeric) and avg weight
```{r controlling for avgweight and covariates modul, echo=TRUE}
metrics=c("Pearson", "Spearman", "Coherence", "WaveletCoherence", "MutualInformation","MutualInformationTime")
#calculate the relationship between modularity and motion controlling for avg weight
for (i in 1:4){
  assign("data",get(paste0("alldata",i)))
  pcorr_modul_estimate=numeric(6)
  for (l in 1:6){
    assign("metric", metrics[l])
    temp <- data %>% dplyr::select(.,matches(paste0("_",metric,"$")),matches("motion"), matches("Age_numeric"),matches("Gender_numeric"))
    print(colnames(temp))
    temp2 <- cbind(temp[1], temp$Age_numeric, temp$Gender_numeric)
    pcorr_modul_estimate[l] <- as.numeric(pcor.test(temp[2], temp$motion, temp2, method = "pearson")$estimate)
  }
  assign(paste0("pcorr_modul_estimate_run",i),data.frame(pcorr_modul_estimate, metrics))
}

#average them together
averaged_pcormotion_allcovariates_acrossruns <-(pcorr_modul_estimate_run1$pcorr_modul_estimate+pcorr_modul_estimate_run2$pcorr_modul_estimate+pcorr_modul_estimate_run3$pcorr_modul_estimate+pcorr_modul_estimate_run4$pcorr_modul_estimate)/4
averaged_pcormotion_allcovariates_acrossruns <- as.data.frame(averaged_pcormotion_allcovariates_acrossruns)
averaged_pcormotion_allcovariates_acrossruns$names <- metrics

barplot(averaged_pcormotion_allcovariates_acrossruns$averaged_pcormotion_allcovariates_acrossruns, names.arg =averaged_pcormotion_allcovariates_acrossruns$names, ylim=c(0.01, -0.08), col="darkblue", cex.axis=1.5, cex.names=1)

#melt them all together
all <- cbind(pcorr_modul_estimate_run1, pcorr_modul_estimate_run2, pcorr_modul_estimate_run3, pcorr_modul_estimate_run4)
all$metrics <- factor(all$metrics, levels=c("Pearson", "Spearman", "Coherence", "WaveletCoherence", "MutualInformation","MutualInformationTime"), labels=c("P", "S", "MIT", "C","WC", "MIF") )
colnames(all) <- c("estimate1", "metrics", "estimate2","metrics", "estimate3", "metrics","estimate4", "metrics")
all <- melt(all, id.vars = "metrics")

#Plot them like Arun, using his colors
p<-ggplot(all, aes(x=metrics, y=value, color=metrics)) + 
  geom_jitter(position=position_jitter(0), cex=1)
p + theme_classic() + stat_summary(fun.data="mean_sdl",fun.args = list(mult = 1) ,
                 geom="pointrange", shape=95, cex=1) + labs(title="333-node Gordon parcellation",x="", y = "Partial correlation of Q with motion")+ theme(plot.title = element_text(hjust = 0.5), legend.position = "none")+ theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14)) +scale_color_manual(values=c("#0072BD", "#D95319", "#EDB120", "#7E2F8E", "#77AC30", "#4DBEEE"))+geom_hline(yintercept = 0)
```

# Null models
## Load in nulls

```{r load null data, include=FALSE}
data_dir="~/Documents/projects/in_progress/arun_fc_metrics_motion/"
dropbox_data="~/Dropbox/projects/in_progress/arun_fc_metrics_motion/output/data/Gordon_ICA_FIX/with_nulls/"
null_run1_data=readMat(paste0(dropbox_data, "nullmodul_withnulls_run1.mat"))
null_run1_data <- data.frame(matrix(unlist(null_run1_data$null.modul, use.names = FALSE), nrow=length(null_run1_data$null.modul[[1]]), byrow=F))
colnames(null_run1_data) <- c('Coherence', 'MutualInformation', 'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
null_run2_data=readMat(paste0(dropbox_data, "nullmodul_withnulls_run2.mat"))
null_run2_data <- data.frame(matrix(unlist(null_run2_data$null.modul, use.names = FALSE), nrow=length(null_run2_data$null.modul[[1]]), byrow=F))
colnames(null_run2_data) <- c('Coherence', 'MutualInformation', 'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
null_run3_data=readMat(paste0(dropbox_data, "nullmodul_withnulls_run3.mat"))
null_run3_data <- data.frame(matrix(unlist(null_run3_data$null.modul, use.names = FALSE), nrow=length(null_run3_data$null.modul[[1]]), byrow=F))
colnames(null_run3_data) <- c('Coherence', 'MutualInformation', 'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
null_run4_data=readMat(paste0(dropbox_data, "nullmodul_withnulls_run4.mat"))
null_run4_data <- data.frame(matrix(unlist(null_run4_data$null.modul, use.names = FALSE), nrow=length(null_run4_data$null.modul[[1]]), byrow=F))
colnames(null_run4_data) <- c('Coherence', 'MutualInformation', 'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
#merge them with the original data files so that they have the right number of submects
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_LR/"
motiondata1 <- read.csv(paste0(mydir,"/rfMRI_REST1_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data1 <- data.frame(subject_list, null_run1_data)
null_alldata1 <- merge(modul_data1, alldata1, by = "subject", all = TRUE)
null_alldata1 <- null_alldata1 %>% filter(., Pearson != 0)
#recode age to be the median of the bins that are provided
#null_alldata1$Age_numeric <- dplyr::recode(null_alldata1$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_RL/"
motiondata2 <- read.csv(paste0(mydir,"/rfMRI_REST1_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data2 <- data.frame(subject_list, null_run2_data)
null_alldata2 <- merge(modul_data2, alldata2, by = "subject", all = TRUE)
null_alldata2 <- null_alldata2 %>% filter(., Pearson != 0)
#recode age to be the median of the bins that are provided
#null_alldata2$Age_numeric <- dplyr::recode(null_alldata2$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_LR/"
motiondata3 <- read.csv(paste0(mydir,"/rfMRI_REST2_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data3 <- data.frame(subject_list, null_run3_data)
null_alldata3 <- merge(modul_data3, alldata3, by = "subject", all = TRUE)
null_alldata3 <- null_alldata3 %>% filter(., Pearson != 0)
null_alldata3 <- na.omit(null_alldata3)
#recode age to be the median of the bins that are provided
#null_alldata3$Age_numeric <- dplyr::recode(null_alldata3$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_RL/"
motiondata4 <- read.csv(paste0(mydir,"/rfMRI_REST2_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data4 <- data.frame(subject_list, null_run4_data)
null_alldata4 <- merge(modul_data4, alldata4, by = "subject", all = TRUE)
null_alldata4 <- null_alldata4 %>% filter(.,Pearson != 0)
null_alldata4 <- na.omit(null_alldata4)
```

## Compare raw modularity to nulls calculated for each metric

```{r plot of raw modularity across different metrics}
metrics=c("Pearson", "Spearman", "Coherence", "WaveletCoherence", "MutualInformation","MutualInformationTime")
#calculate the relationship between raw modularity and motion for each of the 4 runs
for (i in 1:4){
  assign("data",get(paste0("null_alldata",i)))
  null_modul=numeric(6)
   for (l in 1:6){
    assign("metric", metrics[l])
    temp <- data %>% dplyr::select(.,matches(paste0("^",metric,"$")))
    #print(colnames(temp))
    # temp2 <- cbind(temp$Age_numeric, temp[3])
    null_modul[l]<- mean(temp[,1])
     
   }
    assign(paste0("null_modul_estimate_run",i),data.frame(null_modul, metrics))
}
#create an id variable in the all dataframe created earlier
all$type <- "empirical"
#Melt them together
all_null <- cbind(null_modul_estimate_run1, null_modul_estimate_run2, null_modul_estimate_run3, null_modul_estimate_run4)
all_null$metrics <- factor(all_null$metrics, levels=c("Pearson", "Spearman", "Coherence", "WaveletCoherence", "MutualInformation","MutualInformationTime"), labels=c("P", "S", "MIT", "C","WC", "MIF") )
colnames(all_null) <- c("estimate1", "metrics", "estimate2","metrics", "estimate3", "metrics","estimate4", "metrics")
all_null$type <- "null"
all_null <- melt(all_null, id.vars = c("metrics", "type"))
everything <- rbind(all,all_null)
#Plot them like Arun, using his colors
p<-ggplot(everything, aes(x=metrics, y=value, color=type)) + 
  geom_jitter(position=position_jitter(0.2), cex=2.5)
p + theme_classic() + stat_summary(fun.data="mean_sdl",fun.args = list(mult = 1) ,
                 geom="pointrange", shape=95, cex=1) + labs(title="333-node Gordon parcellation",x="", y = "Modularity quality index (Q)")+ theme(plot.title = element_text(hjust = 0.5), legend.position = "none")+ theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14)) +scale_color_manual(values=c("#0072BD", "#D95319", "#EDB120", "#7E2F8E", "#77AC30", "#4DBEEE"))
```

# Run 1
Skip this part after it's done once for each:
```{r read in txt motion files and write them out, include=FALSE}
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_RL/"
myfiles <- list.files(mydir, full.names = TRUE, pattern = "*.txt")
mytxts <- lapply(myfiles, readLines)
mytxts1lines <- unlist(mytxts)
mytxtsdf <- data.frame(filename = basename(myfiles),fulltext = mytxts1lines)
x <- colsplit(mytxtsdf$filename, '_', names =  c('subject','Movement', 'RMS','mean.txt'))
mytxtsdf$subject <- x$subject
mytxtsdf <- mytxtsdf %>% dplyr::select(., c("subject", "fulltext"))
# write it out
write.table(mytxtsdf, file = paste0(mydir, "/rfMRI_REST2_RL.csv"), sep = ",", row.names = FALSE, col.names = FALSE, quote = FALSE)
```

```{r load data, include=FALSE}
data_dir="~/Documents/projects/in_progress/arun_fc_metrics_motion/"
dropbox_data="~/Dropbox/projects/in_progress/arun_fc_metrics_motion/output/data/Gordon_ICA_FIX/"

runs=c("REST1_LR", "REST1_RL")
metrics=c("Pearson", "Spearman", "Coherence", "WaveletCoherence", "MutualInformation","MutualInformationTime")
run1_data=read.csv(paste0(dropbox_data, "modularity_raw_REST1_LR_060319.csv"))
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
```


```{r clean data, include=FALSE}
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_LR/"
motiondata <- read.csv(paste0(mydir,"/rfMRI_REST1_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data <- data.frame(subject_list, run1_data)
alldata <- merge(modul_data, motiondata, by = "subject", all = TRUE)
alldata <- alldata %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
alldata$Age_numeric <- dplyr::recode(alldata$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=38)
dim(alldata)
```
Check dim for number of subjects here, to see if it is the same as that that Arun has for each of the 4 runs.

```{r summary, echo=TRUE}
#summary(alldata)
```

## Avg weight and motion

```{r avgweight motion, echo=TRUE}
#For each of the 6 metrics, plot the correlation between the average weight and motion
par(mfrow=c(2,3))

myPlot<-function(index) {
  plot(alldata[,index] ~ alldata$motion, main=names(alldata[index]),pch=16,xlab="Motion",ylab=names(alldata)[index])
       }
lapply(6:11,FUN=myPlot)
#calculate the correlation between average weight and motion
formulaeAsText <- paste(names(alldata)[6:11], " ~ motion", sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
rawcorr_avgweight<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
rawcorr_avgweight_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
rawmotioncorr <- data.frame(names(alldata)[6:11], unlist(rawcorr_avgweight_sigmotion))
rawmotioncorr
```
## Raw modularity and motion

```{r modularity motion, echo=TRUE}
#For each of the 6 metrics, plot the correlation between the raw modularity metrics calculated when tuning for 7 communities and motion
par(mfrow=c(2,3))

myPlot<-function(index) {
  plot(alldata[,index] ~ alldata$motion, main=names(alldata[index]),pch=19,xlab="Motion", col= "blue",ylab=names(alldata)[index])
       }
lapply(12:17,FUN=myPlot)

#calculate the relationship between raw modularity and motion
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion", sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
rawcorr_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
rawcorr_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
rawmotionmodul_corr <- data.frame(names(alldata)[12:17], unlist(rawcorr_modul_sigmotion))
rawmotionmodul_corr
```

## Modularity and motion, controlling for avg weight
```{r controlling for avgweight modul, echo=TRUE}
#calculate the relationship between modularity and motion controlling for avg weight
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr <- data.frame(names(alldata)[12:17], unlist(corr_modul_sigmotion))
motionmodul_corr
```

## Modularity and motion, controlling for all covariates
```{r controlling for avgweight and covariates modul, echo=TRUE}
#calculate the relationship between modularity and motion controlling for avg weight
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + Age_numeric + Gender + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_covary_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_covary_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr_covary <- data.frame(names(alldata)[12:17], unlist(corr_covary_modul_sigmotion))
motionmodul_corr_covary
```

## Is this affected by differences in number of communities detected across subjects and metrics?

Are the number of communities correlated with motion? And then, does the same pattern of sig relationships present if controlling for number of communities detected for each subject?
```{r number of communities found per subject, echo=TRUE}
#calculate the relationship between motion and number of communities detected
formulaeAsText <- paste(names(alldata)[18:23], " ~ motion + avgweight_",unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_numcomms<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_numcomms_sigmotion<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
numcomms_corr <- data.frame(names(alldata)[12:17], unlist(corr_numcomms_sigmotion))
numcomms_corr

#calculate the relationship between modularity and motion also controlling for the number of communities found for each subject
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + Age_numeric + Gender + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], "+ num_communities_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_covary2_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_covary2_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr2_covary <- data.frame(names(alldata)[12:17], unlist(corr_covary2_modul_sigmotion))
motionmodul_corr2_covary
```

# Run 2
```{r load data 2, include=FALSE}
data_dir="~/Documents/projects/in_progress/arun_fc_metrics_motion/"
dropbox_data="~/Dropbox/projects/in_progress/arun_fc_metrics_motion/output/data/Gordon_ICA_FIX/"
run1_data=read.csv(paste0(dropbox_data, "modularity_raw_REST1_RL_060319.csv"))
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
```

```{r clean data 2, include=FALSE}
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_RL/"
motiondata <- read.csv(paste0(mydir,"/rfMRI_REST1_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data <- data.frame(subject_list, run1_data)
alldata <- merge(modul_data, motiondata, by = "subject", all = TRUE)
alldata <- alldata %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
alldata$Age_numeric <- dplyr::recode(alldata$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=38)
dim(alldata)
```
## Avg weight and motion

```{r avgweight motion 2, echo=TRUE}
#For each of the 6 metrics, plot the correlation between the average weight and motion
par(mfrow=c(2,3))

myPlot<-function(index) {
  plot(alldata[,index] ~ alldata$motion, main=names(alldata[index]),pch=16,xlab="Motion",ylab=names(alldata)[index])
       }
lapply(6:11,FUN=myPlot)
#calculate the correlation between average weight and motion
formulaeAsText <- paste(names(alldata)[6:11], " ~ motion", sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
rawcorr_avgweight<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
rawcorr_avgweight_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
rawmotioncorr <- data.frame(names(alldata)[6:11], unlist(rawcorr_avgweight_sigmotion))
rawmotioncorr
```
## Raw modularity and motion

```{r modularity motion 2, echo=TRUE}
#For each of the 6 metrics, plot the correlation between the raw modularity metrics calculated when tuning for 7 communities and motion
par(mfrow=c(2,3))
myPlot<-function(index) {
  plot(alldata[,index] ~ alldata$motion, main=names(alldata[index]),pch=19,xlab="Motion", col= "blue",ylab=names(alldata)[index])
       }
lapply(12:17,FUN=myPlot)

#calculate the relationship between raw modularity and motion
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion", sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
rawcorr_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
rawcorr_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
rawmotionmodul_corr <- data.frame(names(alldata)[12:17], unlist(rawcorr_modul_sigmotion))
rawmotionmodul_corr
```

## Modularity and motion, controlling for avg weight
```{r controlling for avgweight modul 2, echo=TRUE}
#calculate the relationship between modularity and motion controlling for avg weight
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr <- data.frame(names(alldata)[12:17], unlist(corr_modul_sigmotion))
motionmodul_corr
```

## Modularity and motion, controlling for all covariates
```{r controlling for avgweight and covariates modul 2, echo=TRUE}
#calculate the relationship between modularity and motion controlling for avg weight
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + Age_numeric + Gender + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_covary_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_covary_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr_covary <- data.frame(names(alldata)[12:17], unlist(corr_covary_modul_sigmotion))
motionmodul_corr_covary
```

## Is this affected by differences in number of communities detected across subjects and metrics?
Are the number of communities correlated with motion? And then, does the same pattern of sig relationships present if controlling for number of communities detected for each subject?
```{r number of communities found per subject 2, echo=TRUE}
#calculate the relationship between motion and number of communities detected
formulaeAsText <- paste(names(alldata)[18:23], " ~ motion + avgweight_",unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_numcomms<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_numcomms_sigmotion<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
numcomms_corr <- data.frame(names(alldata)[12:17], unlist(corr_numcomms_sigmotion))
numcomms_corr

#calculate the relationship between modularity and motion also controlling for the number of communities found for each subject
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + Age_numeric + Gender + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], "+ num_communities_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_covary2_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_covary2_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr2_covary <- data.frame(names(alldata)[12:17], unlist(corr_covary2_modul_sigmotion))
motionmodul_corr2_covary
```
# Run 3

```{r load data 3, include=FALSE}
run1_data=read.csv(paste0(dropbox_data, "modularity_raw_REST2_LR_060319.csv"))
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
```

```{r clean data 3, include=FALSE}
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_LR/"
motiondata <- read.csv(paste0(mydir,"/rfMRI_REST2_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data <- data.frame(subject_list, run1_data)
alldata <- merge(modul_data, motiondata, by = "subject", all = TRUE)
alldata <- alldata %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
alldata$Age_numeric <- dplyr::recode(alldata$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=38)
dim(alldata)
```
## Avg weight and motion

```{r avgweight and motion 3, echo=TRUE}
#For each of the 6 metrics, plot the correlation between the average weight and motion
par(mfrow=c(2,3))

myPlot<-function(index) {
  plot(alldata[,index] ~ alldata$motion, main=names(alldata[index]),pch=16,xlab="Motion",ylab=names(alldata)[index])
       }
lapply(6:11,FUN=myPlot)
#calculate the correlation between average weight and motion
formulaeAsText <- paste(names(alldata)[6:11], " ~ motion", sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
rawcorr_avgweight<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
rawcorr_avgweight_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
rawmotioncorr <- data.frame(names(alldata)[6:11], unlist(rawcorr_avgweight_sigmotion))
rawmotioncorr
```
## Raw modularity and motion

```{r modularity and motion 3, echo=TRUE}
#For each of the 6 metrics, plot the correlation between the raw modularity metrics calculated when tuning for 7 communities and motion
par(mfrow=c(2,3))
myPlot<-function(index) {
  plot(alldata[,index] ~ alldata$motion, main=names(alldata[index]),pch=19,xlab="Motion", col= "blue",ylab=names(alldata)[index])
       }
lapply(12:17,FUN=myPlot)

#calculate the relationship between raw modularity and motion
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion", sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
rawcorr_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
rawcorr_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
rawmotionmodul_corr <- data.frame(names(alldata)[12:17], unlist(rawcorr_modul_sigmotion))
rawmotionmodul_corr
```

## Modularity and motion, controlling for avg weight
```{r controlling for avgweight modul 3, echo=TRUE}
#calculate the relationship between modularity and motion controlling for avg weight
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr <- data.frame(names(alldata)[12:17], unlist(corr_modul_sigmotion))
motionmodul_corr
```

## Modularity and motion, controlling for all covariates
```{r controlling for avgweight and covariates modul 3, echo=TRUE}
#calculate the relationship between modularity and motion controlling for avg weight
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + Age_numeric + Gender + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_covary_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_covary_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr_covary <- data.frame(names(alldata)[12:17], unlist(corr_covary_modul_sigmotion))
motionmodul_corr_covary
```

## Is this affected by differences in number of communities detected across subjects and metrics?
Are the number of communities correlated with motion? And then, does the same pattern of sig relationships present if controlling for number of communities detected for each subject?
```{r number of communities found per subject 3, echo=TRUE}
#calculate the relationship between motion and number of communities detected
formulaeAsText <- paste(names(alldata)[18:23], " ~ motion + avgweight_",unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_numcomms<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_numcomms_sigmotion<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
numcomms_corr <- data.frame(names(alldata)[12:17], unlist(corr_numcomms_sigmotion))
numcomms_corr

#calculate the relationship between modularity and motion also controlling for the number of communities found for each subject
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + Age_numeric + Gender + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], "+ num_communities_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_covary2_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_covary2_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr2_covary <- data.frame(names(alldata)[12:17], unlist(corr_covary2_modul_sigmotion))
motionmodul_corr2_covary
```

# Run 4
```{r load data 4, include=FALSE}
run1_data=read.csv(paste0(dropbox_data, "modularity_raw_REST2_RL_060319.csv"))
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
```

```{r clean data 4, include=FALSE}
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_RL/"
motiondata <- read.csv(paste0(mydir,"/rfMRI_REST2_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data <- data.frame(subject_list, run1_data)
alldata <- merge(modul_data, motiondata, by = "subject", all = TRUE)
alldata <- alldata %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
alldata$Age_numeric <- dplyr::recode(alldata$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=38)
dim(alldata)
```
## Avg weight and motion

```{r avgweight and motion 4, echo=TRUE}
#For each of the 6 metrics, plot the correlation between the average weight and motion
par(mfrow=c(2,3))

myPlot<-function(index) {
  plot(alldata[,index] ~ alldata$motion, main=names(alldata[index]),pch=16,xlab="Motion",ylab=names(alldata)[index])
       }
lapply(6:11,FUN=myPlot)
#calculate the correlation between average weight and motion
formulaeAsText <- paste(names(alldata)[6:11], " ~ motion", sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
rawcorr_avgweight<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
rawcorr_avgweight_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
rawmotioncorr <- data.frame(names(alldata)[6:11], unlist(rawcorr_avgweight_sigmotion))
rawmotioncorr
```
## Raw modularity and motion

```{r modularity and motion, echo=TRUE}
#For each of the 6 metrics, plot the correlation between the raw modularity metrics calculated when tuning for 7 communities and motion
par(mfrow=c(2,3))
myPlot<-function(index) {
  plot(alldata[,index] ~ alldata$motion, main=names(alldata[index]),pch=19,xlab="Motion", col= "blue",ylab=names(alldata)[index])
       }
lapply(12:17,FUN=myPlot)

#calculate the relationship between raw modularity and motion
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion", sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
rawcorr_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
rawcorr_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
rawmotionmodul_corr <- data.frame(names(alldata)[12:17], unlist(rawcorr_modul_sigmotion))
rawmotionmodul_corr
```

## Modularity and motion, controlling for avg weight
```{r controlling for avgweight modul 4, echo=TRUE}
#calculate the relationship between modularity and motion controlling for avg weight
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr <- data.frame(names(alldata)[12:17], unlist(corr_modul_sigmotion))
motionmodul_corr
```

## Modularity and motion, controlling for all covariates
```{r controlling for avgweight and covariates modul 4, echo=TRUE}
#calculate the relationship between modularity and motion controlling for avg weight
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + Age_numeric + Gender + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_covary_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_covary_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr_covary <- data.frame(names(alldata)[12:17], unlist(corr_covary_modul_sigmotion))
motionmodul_corr_covary
```

## Is this affected by differences in number of communities detected across subjects and metrics?
Are the number of communities correlated with motion? And then, does the same pattern of sig relationships present if controlling for number of communities detected for each subject?
```{r number of communities found per subject 4, echo=TRUE}
#calculate the relationship between motion and number of communities detected
formulaeAsText <- paste(names(alldata)[18:23], " ~ motion + avgweight_",unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_numcomms<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_numcomms_sigmotion<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
numcomms_corr <- data.frame(names(alldata)[12:17], unlist(corr_numcomms_sigmotion))

#calculate the relationship between modularity and motion also controlling for the number of communities found for each subject
formulaeAsText <- paste(names(alldata)[12:17], " ~ motion + Age_numeric + Gender + avgweight_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], "+ num_communities_", unlist(strsplit(names(alldata)[12:17], "_"))[2*(1:length(names(alldata[,12:17])))], sep="")
formulae <- lapply(formulaeAsText,FUN=formula)
corr_covary2_modul<- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))})
corr_covary2_modul_sigmotion <- lapply(formulae, function(eachFormula) {summary(lm(eachFormula,data=alldata))$coefficients[2,4]})
motionmodul_corr2_covary <- data.frame(names(alldata)[12:17], unlist(corr_covary2_modul_sigmotion))
motionmodul_corr2_covary
```

# No-motion Edges
Examine modularity calculated only using the 20% of edges that show the lowest susceptibility to motion.
Run the first two chunks first.
```{r load data, include=FALSE}
data_dir="~/Documents/projects/in_progress/arun_fc_metrics_motion/"
dropbox_data="~/Dropbox/projects/in_progress/arun_fc_metrics_motion/output/data/Gordon_ICA_FIX/nomotion_edges/"
#run 1
nomotion_run1_data=readMat(paste0(dropbox_data, "modul_nomotionedges_run1.mat"))
nomotion_run1_data <- data.frame(matrix(unlist(nomotion_run1_data$modul, use.names = FALSE), nrow=length(nomotion_run1_data$modul[[1]]), byrow=F))
colnames(nomotion_run1_data) <- c('MutualInformation','Coherence',  'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
nomotion_run1_avgweightdata=readMat(paste0(dropbox_data, "modul_nomotionedges_run1.mat"))
nomotion_run1_data <- data.frame(matrix(unlist(nomotion_run1_data$modul, use.names = FALSE), nrow=length(nomotion_run1_data$modul[[1]]), byrow=F))
colnames(nomotion_run1_data) <- c('MutualInformation','Coherence',  'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
#run 2
nomotion_run2_data=readMat(paste0(dropbox_data, "modul_nomotionedges_run2.mat"))
nomotion_run2_data <- data.frame(matrix(unlist(nomotion_run2_data$modul, use.names = FALSE), nrow=length(nomotion_run2_data$modul[[1]]), byrow=F))
colnames(nomotion_run2_data) <- c('MutualInformation','Coherence',  'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
#run 3
nomotion_run3_data=readMat(paste0(dropbox_data, "modul_nomotionedges_run3.mat"))
nomotion_run3_data <- data.frame(matrix(unlist(nomotion_run3_data$modul, use.names = FALSE), nrow=length(nomotion_run3_data$modul[[1]]), byrow=F))
colnames(nomotion_run3_data) <- c('MutualInformation','Coherence',  'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
#run 4
nomotion_run4_data=readMat(paste0(dropbox_data, "modul_nomotionedges_run4.mat"))
nomotion_run4_data <- data.frame(matrix(unlist(nomotion_run4_data$modul, use.names = FALSE), nrow=length(nomotion_run4_data$modul[[1]]), byrow=F))
colnames(nomotion_run4_data) <- c('MutualInformation','Coherence',  'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
#merge them with the original data files so that they have the right number of submects
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_LR/"
motiondata1 <- read.csv(paste0(mydir,"/rfMRI_REST1_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data1 <- data.frame(subject_list, nomotion_run1_data)
nomotion_alldata1 <- merge(modul_data1,motiondata1, by = "subject", all = TRUE)
nomotion_alldata1 <- nomotion_alldata1 %>% filter(., Pearson != 0)
#recode age to be the median of the bins that are provided
nomotion_alldata1$Age_numeric <- dplyr::recode(nomotion_alldata1$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_RL/"
motiondata2 <- read.csv(paste0(mydir,"/rfMRI_REST1_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data2 <- data.frame(subject_list, nomotion_run2_data)
nomotion_alldata2 <- merge(modul_data2, motiondata2, by = "subject", all = TRUE)
nomotion_alldata2 <- nomotion_alldata2 %>% filter(., Pearson != 0)
#recode age to be the median of the bins that are provided
nomotion_alldata2$Age_numeric <- dplyr::recode(nomotion_alldata2$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_LR/"
motiondata3 <- read.csv(paste0(mydir,"/rfMRI_REST2_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data3 <- data.frame(subject_list, nomotion_run3_data)
nomotion_alldata3 <- merge(modul_data3, motiondata3, by = "subject", all = TRUE)
nomotion_alldata3 <- nomotion_alldata3 %>% filter(., Pearson != 0)
nomotion_alldata3 <- na.omit(nomotion_alldata3)
#recode age to be the median of the bins that are provided
nomotion_alldata3$Age_numeric <- dplyr::recode(nomotion_alldata3$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_RL/"
motiondata4 <- read.csv(paste0(mydir,"/rfMRI_REST2_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data4 <- data.frame(subject_list, nomotion_run4_data)
nomotion_alldata4 <- merge(modul_data4, motiondata4, by = "subject", all = TRUE)
nomotion_alldata4 <- nomotion_alldata4 %>% filter(.,Pearson != 0)
nomotion_alldata4 <- na.omit(nomotion_alldata4)
nomotion_alldata4$Age_numeric <- dplyr::recode(nomotion_alldata4$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
```


## Just plot raw modularity across metrics

```{r plot of raw lowmotion modularity}
#Make a barplot of abs value modularity
toplot <- dplyr::select(rerank_alldata4,Pearson, Spearman, modul_Coherence:modul_MutualInformationTime) 
toplot <- melt(toplot)
p<-ggplot(toplot, aes(x=variable, y=value, fill=variable)) + 
  geom_bar(width = 0.4, position = position_dodge(width=0.5), stat="summary", fun.y=mean)+ 
  theme_classic() 
p
+ labs(title="100-node Yeo parcellation",x="Baseline Edge weight distribution", y = "Modularity quality index Q")+ theme(plot.title = element_text(hjust = 0.5))+ theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))

metrics=c('MutualInformation','Coherence',  'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
#calculate the relationship between raw modularity and motion for each of the 4 runs
for (i in 1:4){
  assign("data",get(paste0("nomotion_alldata",i)))
  rawcorr_modul_estimate=numeric(6)
   for (l in 1:6){
    assign("metric", metrics[l])
    temp <- data %>% dplyr::select(.,matches(paste0("^",metric,"$")),matches("motion"), matches("Gender"),matches("Age_numeric"))
    print(colnames(temp))
    temp2 <- cbind(temp$Age_numeric, temp[3])
    pcorr_modul[l]<- mean(temp[,1])
   }
    assign(paste0("pcorr_modul_estimate_run",i),data.frame(pcorr_modul, metrics))
}
#beeswarm plot
#Melt them together
all <- cbind(pcorr_modul_estimate_run1, pcorr_modul_estimate_run2, pcorr_modul_estimate_run3, pcorr_modul_estimate_run4)
all$metrics <- factor(all$metrics, levels=c('MutualInformation','Coherence',  'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence'), labels=c("MI", "C", "MIT", "P", "S","WC") )
colnames(all) <- c("estimate1", "metrics", "estimate2","metrics", "estimate3", "metrics","estimate4", "metrics")
all <- melt(all, id.vars = "metrics")
#Plot them like Arun, using his colors
p<-ggplot(all, aes(x=metrics, y=value, color=metrics)) + 
  geom_jitter(position=position_jitter(0), cex=2)
p + theme_classic() + stat_summary(fun.data="mean_sdl",fun.args = list(mult = 1) ,
                 geom="pointrange", shape=18, cex=1.3) + labs(title="333-node Gordon parcellation",x="", y = "Modularity quality index (Q)")+ theme(plot.title = element_text(hjust = 0.5))+ theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14)) +scale_color_manual(values=c("#0072BD", "#D95319", "#EDB120", "#7E2F8E", "#77AC30", "#4DBEEE"))
```

## No motion modularity and motion correlations, controlling for age

```{r modularity motion, echo=TRUE}
metrics=c('MutualInformation','Coherence',  'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence')
#calculate the relationship between raw modularity and motion for each of the 4 runs
for (i in 1:4){
  assign("data",get(paste0("nomotion_alldata",i)))
  rawcorr_modul_estimate=numeric(6)
   for (l in 1:6){
    assign("metric", metrics[l])
    temp <- data %>% dplyr::select(.,matches(paste0("^",metric,"$")),matches("motion"), matches("Gender"),matches("Age_numeric"))
    print(colnames(temp))
    temp2 <- cbind(temp$Age_numeric, temp[3])
    pcorr_modul[l]<- as.numeric(pcor.test(temp[1], temp[2],temp[4], method="kendall")$estimate)
   }
    assign(paste0("pcorr_modul_estimate_run",i),data.frame(pcorr_modul, metrics))
}

#beeswarm plot
#Melt them together
all <- cbind(pcorr_modul_estimate_run1, pcorr_modul_estimate_run2, pcorr_modul_estimate_run3, pcorr_modul_estimate_run4)
all$metrics <- factor(all$metrics, levels=c('MutualInformation','Coherence',  'MutualInformationTime','Pearson','Spearman', 'WaveletCoherence'), labels=c("MI", "C", "MIT", "P", "S","WC") )
colnames(all) <- c("estimate1", "metrics", "estimate2","metrics", "estimate3", "metrics","estimate4", "metrics")
all <- melt(all, id.vars = "metrics")
#Plot them like Arun, using his colors
p<-ggplot(all, aes(x=metrics, y=value, color=metrics)) + 
  geom_jitter(position=position_jitter(0), cex=2)
p + theme_classic() + stat_summary(fun.data="mean_sdl",fun.args = list(mult = 1) ,
                 geom="pointrange", shape=18, cex=1.3) + labs(title="333-node Gordon parcellation",x="", y = "Partial corr of Q with motion, low-motion edges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14)) +scale_color_manual(values=c("#0072BD", "#D95319", "#EDB120", "#7E2F8E", "#77AC30", "#4DBEEE"))+geom_hline(yintercept = 0)
```

## No motion modularity and motion correlations, controlling for age AND avg weight

