---
title: "FC Metrics Susceptibility to Motion- Reranked Edge Weights"
output:
  html_document:
    theme: united
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(psych)
library(gam)
library(summarytools)
library(PerformanceAnalytics)
library(ppcor)
library(reshape2)
library(R.matlab)
```

# Schaefer Parcellation
## Import original data and merge in

```{r load data, include=FALSE}
data_dir="~/Documents/projects/in_progress/arun_fc_metrics_motion/"
dropbox_data="~/Dropbox/projects/in_progress/arun_fc_metrics_motion/output/data/Schaefer100_ICA_FIX/"
run1_data=read.csv(paste0(dropbox_data, "modularity_raw_REST1_LR_062419.csv"))
run2_data=read.csv(paste0(dropbox_data, "modularity_raw_REST1_RL_062419.csv"))
run3_data=read.csv(paste0(dropbox_data, "modularity_raw_REST2_LR_062419.csv"))
run4_data=read.csv(paste0(dropbox_data, "modularity_raw_REST2_RL_062419.csv"))
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_LR/"
motiondata1 <- read.csv(paste0(mydir,"/rfMRI_REST1_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data1 <- data.frame(subject_list, run1_data)
alldata1 <- merge(modul_data1, motiondata1, by = "subject", all = TRUE)
alldata1 <- alldata1 %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
alldata1$Age_numeric <- dplyr::recode(alldata1$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_RL/"
motiondata2 <- read.csv(paste0(mydir,"/rfMRI_REST1_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data2 <- data.frame(subject_list, run2_data)
alldata2 <- merge(modul_data2, motiondata2, by = "subject", all = TRUE)
alldata2 <- alldata2 %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
alldata2$Age_numeric <- dplyr::recode(alldata2$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_LR/"
motiondata3 <- read.csv(paste0(mydir,"/rfMRI_REST2_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data3 <- data.frame(subject_list, run3_data)
alldata3 <- merge(modul_data3, motiondata3, by = "subject", all = TRUE)
alldata3 <- alldata3 %>% filter(., num_communities_Pearson != 0)
alldata3 <- na.omit(alldata3)
#recode age to be the median of the bins that are provided
alldata3$Age_numeric <- dplyr::recode(alldata3$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_RL/"
motiondata4 <- read.csv(paste0(mydir,"/rfMRI_REST2_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data4 <- data.frame(subject_list, run4_data)
alldata4 <- merge(modul_data4, motiondata4, by = "subject", all = TRUE)
alldata4 <- alldata4 %>% filter(., num_communities_Pearson != 0)
alldata4 <- na.omit(alldata4)
#recode age to be the median of the bins that are provided
alldata4$Age_numeric <- dplyr::recode(alldata4$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
```

## Import reranked data from .mat files
Merge with orig files.
IMPORTANT: There was a bug in the matlab script which means that later runs have values for modularity for subjects that are not there, because modul was not cleared out between loops. This only applies to the re-ranked matrices run using the Schaefer parcellation, which were run all in one loop, so here we avoid it by merging into the original files which have the right number of subjects.
```{r load data, include=FALSE}
data_dir="~/Documents/projects/in_progress/arun_fc_metrics_motion/"
dropbox_data="~/Dropbox/projects/in_progress/arun_fc_metrics_motion/output/data/Schaefer100_ICA_FIX/reranked_matrices/"
rerank_run1_data=readMat(paste0(dropbox_data, "modul_run1.mat"))
rerank_run1_data <- data.frame(matrix(unlist(rerank_run1_data$modul, use.names = FALSE), nrow=length(rerank_run1_data$modul[[1]][[1]]), byrow=F))
colnames(rerank_run1_data) <- c("Pearson.Pearson", "Pearson.WaveletCoherence", "WaveletCoherence.Pearson", "WaveletCoherence.WaveletCoherence")
rerank_run2_data=readMat(paste0(dropbox_data, "modul_run2.mat"))
rerank_run2_data <- data.frame(matrix(unlist(rerank_run2_data$modul, use.names = FALSE), nrow=length(rerank_run2_data$modul[[1]][[1]]), byrow=F))
colnames(rerank_run2_data) <- c("Pearson.Pearson", "Pearson.WaveletCoherence", "WaveletCoherence.Pearson", "WaveletCoherence.WaveletCoherence")
rerank_run3_data=readMat(paste0(dropbox_data, "modul_run3.mat"))
rerank_run3_data <- data.frame(matrix(unlist(rerank_run3_data$modul, use.names = FALSE), nrow=length(rerank_run3_data$modul[[1]][[1]]), byrow=F))
colnames(rerank_run3_data) <- c("Pearson.Pearson", "Pearson.WaveletCoherence", "WaveletCoherence.Pearson", "WaveletCoherence.WaveletCoherence")
rerank_run4_data=readMat(paste0(dropbox_data, "modul_run4.mat"))
rerank_run4_data <- data.frame(matrix(unlist(rerank_run4_data$modul, use.names = FALSE), nrow=length(rerank_run4_data$modul[[1]][[1]]), byrow=F))
colnames(rerank_run4_data) <- c("Pearson.Pearson", "Pearson.WaveletCoherence", "WaveletCoherence.Pearson", "WaveletCoherence.WaveletCoherence")
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
#merge them with the original data files so that they have the right number of submects
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_LR/"
motiondata1 <- read.csv(paste0(mydir,"/rfMRI_REST1_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data1 <- data.frame(subject_list, rerank_run1_data)
rerank_alldata1 <- merge(modul_data1, alldata1, by = "subject", all = TRUE)
rerank_alldata1 <- rerank_alldata1 %>% filter(., Pearson.Pearson != 0)
#recode age to be the median of the bins that are provided
#rerank_alldata1$Age_numeric <- dplyr::recode(rerank_alldata1$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_RL/"
motiondata2 <- read.csv(paste0(mydir,"/rfMRI_REST1_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data2 <- data.frame(subject_list, rerank_run2_data)
rerank_alldata2 <- merge(modul_data2, alldata2, by = "subject", all = TRUE)
rerank_alldata2 <- rerank_alldata2 %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
#rerank_alldata2$Age_numeric <- dplyr::recode(rerank_alldata2$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_LR/"
motiondata3 <- read.csv(paste0(mydir,"/rfMRI_REST2_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data3 <- data.frame(subject_list, rerank_run3_data)
rerank_alldata3 <- merge(modul_data3, alldata3, by = "subject", all = TRUE)
rerank_alldata3 <- rerank_alldata3 %>% filter(., num_communities_Pearson != 0)
rerank_alldata3 <- na.omit(rerank_alldata3)
#recode age to be the median of the bins that are provided
#rerank_alldata3$Age_numeric <- dplyr::recode(rerank_alldata3$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_RL/"
motiondata4 <- read.csv(paste0(mydir,"/rfMRI_REST2_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data4 <- data.frame(subject_list, rerank_run4_data)
rerank_alldata4 <- merge(modul_data4, alldata4, by = "subject", all = TRUE)
rerank_alldata4 <- rerank_alldata4 %>% filter(.,num_communities_Pearson != 0)
rerank_alldata4 <- na.omit(rerank_alldata4)
```

## Check how modularity calculated on reranked matrices compares to that of the original

```{r modularity motion, echo=TRUE}
#Compare modularity q on Pearson reranked into wavelet coherence to wavelet coherence itself
for (i in 1:4){
  assign("dataorig",get(paste0("alldata",i)))
  print(summary(dataorig$modul_WaveletCoherence))
  assign("data",get(paste0("rerank_alldata",i)))
  #print(summary(data$WaveletCoherence.Pearson)) #look just at which ones are higher, the original or the re-ranked?
  #cycle through Pearson and Wavelet Coherence
}
```

## See how much Q is correlated with motion for the reranked vs. original
```{r controlling for avgweight modul, echo=TRUE}
for (i in 1:4){
  assign("dataorig",get(paste0("alldata",i)))
  assign("data",get(paste0("rerank_alldata",i)))
  rawcorr_modul_estimate<- lapply(dataorig[12:17], function(eachFormula) {cor.test(eachFormula, dataorig$motion, method="kendall")}$estimate)
  rerankedcorr_modul_estimate<- lapply(data[7:8], function(eachFormula) {cor.test(eachFormula, data$motion, method="kendall")$estimate})
  rawmotionmodul_corr <- data.frame(names(dataorig)[12:17], unlist(rawcorr_modul_estimate))
  reranked_motion_corr <- data.frame(names(data)[7:8], unlist(rerankedcorr_modul_estimate))
  assign(paste0("rerankedmotion_corr_run",i),rawmotionmodul_corr)
  assign(paste0("rerankedmotion_corr_run",i),reranked_motion_corr)
}

#average them together
reranked_motion_corr_across_runs$estimate <-(rerankedmotion_corr_run1$unlist.rerankedcorr_modul_estimate.+rerankedmotion_corr_run2$unlist.rerankedcorr_modul_estimate. +rerankedmotion_corr_run3$unlist.rerankedcorr_modul_estimate.+rerankedmotion_corr_run4$unlist.rerankedcorr_modul_estimate.)/4
reranked_motion_corr_across_runs$names <- names(rerank_alldata1)[7:8]
barplot(reranked_motion_corr_across_runs$estimate, names.arg =reranked_motion_corr_across_runs$names, ylim=c(0, -0.08), col="magenta", cex.axis=1.5, cex.names=1, main="Correlation between Q and motion for reranked matrices, averaged across runs")
```


# Gordon Parcellation
## Import original data and merge in

```{r load data, include=FALSE}
data_dir="~/Documents/projects/in_progress/arun_fc_metrics_motion/"
dropbox_data="~/Dropbox/projects/in_progress/arun_fc_metrics_motion/output/data/Gordon_ICA_FIX/"
run1_data=read.csv(paste0(dropbox_data, "modularity_raw_REST1_LR_060319.csv"))
run2_data=read.csv(paste0(dropbox_data, "modularity_raw_REST1_RL_060319.csv"))
run3_data=read.csv(paste0(dropbox_data, "modularity_raw_REST2_LR_060319.csv"))
run4_data=read.csv(paste0(dropbox_data, "modularity_raw_REST2_RL_060319.csv"))
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_LR/"
motiondata1 <- read.csv(paste0(mydir,"/rfMRI_REST1_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data1 <- data.frame(subject_list, run1_data)
alldata1 <- merge(modul_data1, motiondata1, by = "subject", all = TRUE)
alldata1 <- alldata1 %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
alldata1$Age_numeric <- dplyr::recode(alldata1$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_RL/"
motiondata2 <- read.csv(paste0(mydir,"/rfMRI_REST1_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data2 <- data.frame(subject_list, run2_data)
alldata2 <- merge(modul_data2, motiondata2, by = "subject", all = TRUE)
alldata2 <- alldata2 %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
alldata2$Age_numeric <- dplyr::recode(alldata2$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_LR/"
motiondata3 <- read.csv(paste0(mydir,"/rfMRI_REST2_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data3 <- data.frame(subject_list, run3_data)
alldata3 <- merge(modul_data3, motiondata3, by = "subject", all = TRUE)
alldata3 <- alldata3 %>% filter(., num_communities_Pearson != 0)
alldata3 <- na.omit(alldata3)
#recode age to be the median of the bins that are provided
alldata3$Age_numeric <- dplyr::recode(alldata3$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_RL/"
motiondata4 <- read.csv(paste0(mydir,"/rfMRI_REST2_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data4 <- data.frame(subject_list, run4_data)
alldata4 <- merge(modul_data4, motiondata4, by = "subject", all = TRUE)
alldata4 <- alldata4 %>% filter(., num_communities_Pearson != 0)
alldata4 <- na.omit(alldata4)
#recode age to be the median of the bins that are provided
alldata4$Age_numeric <- dplyr::recode(alldata4$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
```

## Import reranked data from .mat files
Merge with orig files.
IMPORTANT: There was a bug in the matlab script which means that later runs have values for modularity for subjects that are not there, because modul was not cleared out between loops. This only applies to the re-ranked matrices run using the Schaefer parcellation, which were run all in one loop, so here we avoid it by merging into the original files which have the right number of subjects.
```{r load data, include=FALSE}
data_dir="~/Documents/projects/in_progress/arun_fc_metrics_motion/"
dropbox_data="~/Dropbox/projects/in_progress/arun_fc_metrics_motion/output/data/Schaefer100_ICA_FIX/reranked_matrices/"
rerank_run1_data=readMat(paste0(dropbox_data, "modul_run1.mat"))
rerank_run1_data <- data.frame(matrix(unlist(rerank_run1_data$modul, use.names = FALSE), nrow=length(rerank_run1_data$modul[[1]][[1]]), byrow=F))
colnames(rerank_run1_data) <- c("Pearson.Pearson", "Pearson.WaveletCoherence", "WaveletCoherence.Pearson", "WaveletCoherence.WaveletCoherence")
rerank_run2_data=readMat(paste0(dropbox_data, "modul_run2.mat"))
rerank_run2_data <- data.frame(matrix(unlist(rerank_run2_data$modul, use.names = FALSE), nrow=length(rerank_run2_data$modul[[1]][[1]]), byrow=F))
colnames(rerank_run2_data) <- c("Pearson.Pearson", "Pearson.WaveletCoherence", "WaveletCoherence.Pearson", "WaveletCoherence.WaveletCoherence")
rerank_run3_data=readMat(paste0(dropbox_data, "modul_run3.mat"))
rerank_run3_data <- data.frame(matrix(unlist(rerank_run3_data$modul, use.names = FALSE), nrow=length(rerank_run3_data$modul[[1]][[1]]), byrow=F))
colnames(rerank_run3_data) <- c("Pearson.Pearson", "Pearson.WaveletCoherence", "WaveletCoherence.Pearson", "WaveletCoherence.WaveletCoherence")
rerank_run4_data=readMat(paste0(dropbox_data, "modul_run4.mat"))
rerank_run4_data <- data.frame(matrix(unlist(rerank_run4_data$modul, use.names = FALSE), nrow=length(rerank_run4_data$modul[[1]][[1]]), byrow=F))
colnames(rerank_run4_data) <- c("Pearson.Pearson", "Pearson.WaveletCoherence", "WaveletCoherence.Pearson", "WaveletCoherence.WaveletCoherence")
subject_list=read.csv(paste0(data_dir, "data/subjLists/S1200_Release_Subjects_Demographics.csv"))
subject_list <- subject_list %>% dplyr::select(.,Subject:Age) %>% rename(., subject=Subject)
#merge them with the original data files so that they have the right number of submects
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_LR/"
motiondata1 <- read.csv(paste0(mydir,"/rfMRI_REST1_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data1 <- data.frame(subject_list, rerank_run1_data)
rerank_alldata1 <- merge(modul_data1, alldata1, by = "subject", all = TRUE)
rerank_alldata1 <- rerank_alldata1 %>% filter(., Pearson.Pearson != 0)
#recode age to be the median of the bins that are provided
#rerank_alldata1$Age_numeric <- dplyr::recode(rerank_alldata1$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST1_RL/"
motiondata2 <- read.csv(paste0(mydir,"/rfMRI_REST1_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data2 <- data.frame(subject_list, rerank_run2_data)
rerank_alldata2 <- merge(modul_data2, alldata2, by = "subject", all = TRUE)
rerank_alldata2 <- rerank_alldata2 %>% filter(., num_communities_Pearson != 0)
#recode age to be the median of the bins that are provided
#rerank_alldata2$Age_numeric <- dplyr::recode(rerank_alldata2$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_LR/"
motiondata3 <- read.csv(paste0(mydir,"/rfMRI_REST2_LR.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data3 <- data.frame(subject_list, rerank_run3_data)
rerank_alldata3 <- merge(modul_data3, alldata3, by = "subject", all = TRUE)
rerank_alldata3 <- rerank_alldata3 %>% filter(., num_communities_Pearson != 0)
rerank_alldata3 <- na.omit(rerank_alldata3)
#recode age to be the median of the bins that are provided
#rerank_alldata3$Age_numeric <- dplyr::recode(rerank_alldata3$Age, "22-25"= 23.5, "26-30"=28, "31-35"=33, "36+"=36)
mydir="~/Documents/projects/in_progress/arun_fc_metrics_motion/data/subjData/Motion_S1200/rfMRI_REST2_RL/"
motiondata4 <- read.csv(paste0(mydir,"/rfMRI_REST2_RL.csv"), header = FALSE, col.names = c("subject", "motion"))
modul_data4 <- data.frame(subject_list, rerank_run4_data)
rerank_alldata4 <- merge(modul_data4, alldata4, by = "subject", all = TRUE)
rerank_alldata4 <- rerank_alldata4 %>% filter(.,num_communities_Pearson != 0)
rerank_alldata4 <- na.omit(rerank_alldata4)
```

## Check how modularity calculated on reranked matrices compares to that of the original

```{r modularity motion, echo=TRUE}
#Compare modularity q on Pearson reranked into wavelet coherence to wavelet coherence itself
for (i in 1:4){
  assign("dataorig",get(paste0("alldata",i)))
  print(summary(dataorig$modul_WaveletCoherence))
  assign("data",get(paste0("rerank_alldata",i)))
  #print(summary(data$WaveletCoherence.Pearson)) #look just at which ones are higher, the original or the re-ranked?
  #cycle through Pearson and Wavelet Coherence
}
```

## See how much Q is correlated with motion for the reranked vs. original
```{r controlling for avgweight modul, echo=TRUE}
for (i in 1:4){
  assign("dataorig",get(paste0("alldata",i)))
  assign("data",get(paste0("rerank_alldata",i)))
  rawcorr_modul_estimate<- lapply(dataorig[12:17], function(eachFormula) {cor.test(eachFormula, dataorig$motion, method="kendall")}$estimate)
  rerankedcorr_modul_estimate<- lapply(data[7:8], function(eachFormula) {cor.test(eachFormula, data$motion, method="kendall")$estimate})
  rawmotionmodul_corr <- data.frame(names(dataorig)[12:17], unlist(rawcorr_modul_estimate))
  reranked_motion_corr <- data.frame(names(data)[7:8], unlist(rerankedcorr_modul_estimate))
  assign(paste0("rerankedmotion_corr_run",i),rawmotionmodul_corr)
  assign(paste0("rerankedmotion_corr_run",i),reranked_motion_corr)
}

#average them together
reranked_motion_corr_across_runs$estimate <-(rerankedmotion_corr_run1$unlist.rerankedcorr_modul_estimate.+rerankedmotion_corr_run2$unlist.rerankedcorr_modul_estimate. +rerankedmotion_corr_run3$unlist.rerankedcorr_modul_estimate.+rerankedmotion_corr_run4$unlist.rerankedcorr_modul_estimate.)/4
reranked_motion_corr_across_runs$names <- names(rerank_alldata1)[7:8]
barplot(reranked_motion_corr_across_runs$estimate, names.arg =reranked_motion_corr_across_runs$names, ylim=c(0, -0.08), col="magenta", cex.axis=1.5, cex.names=1, main="Correlation between Q and motion for reranked matrices, averaged across runs")
```
